### 2018-07-05 paper/6-engineering.tex
Polishing (thanks, Andrew!)
Add references on fixed-point/cyclic tasks

\begin{minted}{haskell}
sprsh5 "B1" = Just $ Task $ \fetch -> do
    formula <- fetch "B1-formula"
    evalFormula fetch formula
\end{minted}

% It is not possible to
% change dependencies based on the formula in a \hs{Tasks}~\hs{Applicative}, as
% would be required, so instead the formula can be captured as a dependency
% (but its value not used) and \emph{also} baked directly into the \hs{sprsh5}
% function. \simon{Don't understand.}
% \simon{I think you mean that you can find dependencies with executing the function,
%   which seems quite difference from ``backing it into'' the Haskell code.}

@@

Overall we choose not to deal with cyclic rules, a choice that most build
systems also follow.

>>>>

\begin{minted}{haskell}
sprsh4 "B1" = Just $ Task $ \fetch -> do
    formula <- fetch "B1-formula"
    evalFormula fetch formula
\end{minted}

% It is not possible to
% change dependencies based on the formula in a \hs{Tasks}~\hs{Applicative}, as
% would be required, so instead the formula can be captured as a dependency
% (but its value not used) and \emph{also} baked directly into the \hs{sprsh4}
% function. \simon{Don't understand.}
% \simon{I think you mean that you can find dependencies with executing the function,
%   which seems quite difference from ``backing it into'' the Haskell code.}

@@

Overall we choose not to deal with cyclic dependencies, a choice that most build
systems also follow. There are computation frameworks that support tasks with
cyclic dependencies under the assumption that tasks are \emph{monotonic} in a
certain sense, e.g. see~\cite{pottier2009lazy} and~\cite{radul2009propagation}.
